Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-09 ms.tex
test2
updated abstract

\begin{abstract}
  We calculate the steady-state hydrodynamic profiles of hot gas in
  the nuclei of a sample of early-type quiescent galaxies.  We assume
  that mass is supplied to the circumnuclear medium (CNM) entirely by
  stellar winds according to the radial stellar profiles for each
  galaxy, while the gas is heated by a combination of shocked stellar
  winds and supernovae.  Our analytic and numerical results are used
  to estimate the accretion rates onto the central supermassive black
  holes (SMBH) as a function of the SMBH mass $M_{\bullet}$ and the
  heating efficiency, the latter of which is related schematically to
  the age of the stellar population, the frequency of supernovae, and
  the efficacy of accretion feedback processes.  For a fixed heating
  efficiency, we find that the SMBH accretion Eddington factor
  increases with the SMBH mass, $\dot{M}/\dot{M}_{\rm edd} \propto
  M_{\bullet}^{\alpha}$ with $\alpha \approx 0.5, 1$ for cusp and core
  nuclei, respectively.
  % However, considering the potentially lower heating efficiency of low
  % mass SMBHs (due to a younger stellar population and the rareity of
  % supernovae within the stagnation radius) and their resulting higher
  % susceptibility to cooling instability, we find a flatter
  % relationship $\alpha \approx 0$. 
  Our results are used to check previous estimates of the SMBH
  accretion rate assuming Bondi accretion and extrapolating the X-ray
  measured density and temperature to the unresolved Bondi radius.  We
  also discuss the implications of our results for the diversity of
  CNM environments encountered by the jetted outflows from tidal
  disruption events, and for the use of an assumed
  $\dot{M}-M_{\bullet}$ relationship to constrain the occupation
  fraction of SMBHs in low mass galaxies.
\end{abstract}

>>>>

\begin{abstract}
Steady-state one-dimensional hydrodynamic profiles of hot gas in the nuclei of quiescent galaxies are calculated for a range of black hole masses, parameterized gas heating rates, and physically-motivated stellar density profiles.  Mass is supplied to the circumnuclear medium (CNM) by stellar winds, while gas is heated by a combination of stellar winds, supernovae, and black hole feedback.  Neglecting radiative cooling, analytic estimates are derived for quantities including the stagnation radius where the radial velocity goes to zero (if it exists) and the black hole accretion rate as a function of the heating efficiency, the latter of which is related to the star-formation history of the stellar population.  We assess over what range of conditions radiative instability will develop, assuming a star formation history corresponding to the average of that for galaxies of a given black hole mass.  Our main conclusion is that.....  Implications of our results for estimates of the accretion rate using Bondi formula, and for the diversity of CNM environments encountered by the jetted outflows from tidal disruption events, and for the use of an assumed $\dot{M}-M_{\bullet}$ relationship to constrain the occupation fraction of SMBHs in low mass galaxies, are briefly discussed.
\end{abstract}
